%% start of file `template.tex'.
%% Copyright 2006-2015 Xavier Danaux (xdanaux@gmail.com).
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License version 1.3c,
% available at http://www.latex-project.org/lppl/.


\documentclass[11pt,a4paper,roman]{moderncv}        % possible options include font size ('10pt', '11pt' and '12pt'), paper size ('a4paper', 'letterpaper', 'a5paper', 'legalpaper', 'executivepaper' and 'landscape') and font family ('sans' and 'roman')

% moderncv themes
\moderncvstyle{banking}                             % style options are 'casual' (default), 'classic', 'banking', 'oldstyle' and 'fancy'
\moderncvcolor{blue}                               % color options 'black', 'blue' (default), 'burgundy', 'green', 'grey', 'orange', 'purple' and 'red'
%\renewcommand{\familydefault}{\sfdefault}         % to set the default font; use '\sfdefault' for the default sans serif font, '\rmdefault' for the default roman one, or anyhttps://www.overleaf.com/project/5f844cadbdcfca000112d818 tex font name
%\nopagenumbers{}                                  % uncomment to suppress automatic page numbering for CVs longer than one page

% character encoding
\usepackage[utf8]{inputenc}                       % if you are not using xelatex ou lualatex, replace by the encoding you are using
%\usepackage{CJKutf8}                              % if you need to use CJK to typeset your resume in Chinese, Japanese or Korean

% adjust the page margins
%\usepackage{hyperref}
%\hypersetup{hidelinks}
\usepackage[scale=0.8]{geometry}
%\setlength{\hintscolumnwidth}{3cm}                % if you want to change the width of the column with the dates
%\setlength{\makecvtitlenamewidth}{10cm}           % for the 'classic' style, if you want to force the width allocated to your name and avoid line breaks. be careful though, the length is normally calculated to avoid any overlap with your personal info; use this at your own typographical risks...

% personal data
\name{Lawrence}{Wu}% optional, remove / comment the line if not wanted
\address{St John's College, St John's Street, Cambridge CB2 1TP}% optional, remove / comment the line if not wanted; the "postcode city" and "country" arguments can be omitted or provided empty
\phone[fixed]{(+44)7955105921}                   % optional, remove / comment the line if not wanted; the optional "type" of the phone can be "mobile" (default), "fixed" or "fax"
\email{shw43@cam.ac.uk}                               % optional, remove / comment the line if not wanted                            

% bibliography adjustements (only useful if you make citations in your resume, or print a list of publications using BibTeX)
%   to show numerical labels in the bibliography (default is to show no labels)
\makeatletter\renewcommand*{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}\makeatother
%   to redefine the bibliography heading string ("Publications")
%\renewcommand{\refname}{Articles}

% bibliography with mutiple entries
%\usepackage{multibib}
%\newcites{book,misc}{{Books},{Others}}
%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}
%\begin{CJK*}{UTF8}{gbsn}                          % to typeset your resume in Chinese using CJK
%-----       resume       ---------------------------------------------------------
\makecvtitle

%=========================================================================
%=========================================================================
\section{Education}

\textbf{University of Cambridge} \textit{MSc Physics} \hfill \textit{Oct.2022--Jun.2023}
\vspace*{1mm}
\begin{itemize}
    \item Thesis: Calabi-Yau Metric Approximations using Graph Neural Networks
    \item Quantum Field Theory, Advanced Statistical Physics
\end{itemize}

\vspace*{3mm}


\textbf{University of Cambridge} \textit{BA(Hons) Physics, 1st class} \hfill \textit{Oct.2019--Jun.2022}
\vspace*{1mm}
\begin{itemize}
    \item Scored over 90\% in 2/4 final year core modules (General Relativity, Electrodynamics)
	\item Computing Project: Simulation of the Ising Model of Ferromagnetism
	\item Literature Review: Development of Quantum Computing Hardware\\
\end{itemize}

Relevant Modules: Statistical Physics, Advanced Quantum Mechanics, Particle Physics,\\
Linear Algebra, PDE, Complex Analysis, Group Theory, Rep Theory, Differential Geometry\\

\textbf{West London Free School (UK)} \textit{Sixth Form} \hfill \textit{Oct.2017--Jun.2019}
\vspace*{1mm}
\begin{itemize}
\item{A-Levels (All A*s): Physics, Maths, Further Maths, Chemistry.}
\end{itemize}
\vspace*{3mm}

\textbf{Taipei Municipal Jianguo High School (Taiwan)} \textit{High School}\hfill \textit{Sept.2016--Oct.2017}
\vspace*{1mm}
\begin{itemize}
\item{Ranked 1st in entrance exam for the governmental Gifted Class of Mathematics and Science.}
\end{itemize}

%========================================================================= %=========================================================================
\section{Awards}
\begin{itemize}
	\item United Steel Companies Scholarship, St John's College, University of Cambridge (2020, 2022)
	\item Top Gold, British Physics Olympiad (2019)
  %\item{Golds, UK Senior Math Challenge (2017 \& 2018)}
\end{itemize}


%=========================================================================
%=========================================================================
\section{Publication}
\textbf{Investigation of Cosmic Preferred Directions in the Cosmic Microwave Background Using New Strategies}, Lawrence Wu \& Jiun-Huei Proty Wu (in preparation).

%=========================================================================
%=========================================================================
\section{Research Experience/Projects}

\textbf{Calabi-Yau Metric Approximations using Graph Neural Networks} \hfill \textit{Oct.2022--May.2023}
\vspace*{1mm}\\
{Supervisor: Prof.\ Pietro Lio, Computer Laboratory, University of Cambridge.}
\vspace*{1mm}
\begin{itemize}
	\item Deducing numerical Ricci flat metrics for different C-Y manifolds through GNNs by manifold graph discretisation\\
\end{itemize}

\textbf{Preferred Directions in the Cosmic Microwave Background (CMB)} \hfill \textit{Aug.2021--present}
\vspace*{1mm}\\
{Supervisor: Prof.\ Jiun-Huei Proty Wu, Department of Physics, National Taiwan University.}
\vspace*{1mm}
\begin{itemize}
	\item Independently developed the codebase, which analyses data with over 50 million pixels each
	\item Applied new strategies to investigate possible preferred axes or directions in the observed full-sky CMB maps.\\
\end{itemize}

\textbf{Efficient Wordle Solver based on a Complete Graph} \hfill \textit{Feb. 2022} 
\vspace*{1mm}\\
{Independent research on Interesting Problems}
\vspace*{1mm}
\begin{itemize}
	\item A rapid brute force solver in python based on the complete directed graph of all 6000 5-letter words 
	\item The directed graph was simplified into a simple graph by applying a non-trivial symmetry between the edges
	\item Concluded the best strategy of starting with "Aloes" with an expected guess count of 3.2 guesses\\
\end{itemize}

\textbf{Simulation of the Ising Model} \hfill \textit{Oct.2021--Apr.2022} 
\vspace*{1mm}\\ 
{Undergraduate Computational Project.}
\vspace*{1mm}
\begin{itemize}
	\item Implemented and Investigated the Ising Model using Monte-Carlo optimisation algorithms.\\
\end{itemize}

\textbf{Simulation of the domestic and international spreading of COVID-19} \hfill \textit{Mar.--Jun.2020} 
\vspace*{1mm}\\
{Independent research on Models building.}
\vspace*{1mm}
\begin{itemize}
	\item Simulated the spreading by modelling individuals as repulsive particles.
    \item Investigated how the spreading rate varies with the strictness of quarantining, travel restriction and  social distancing
    \item Determined how the rate of spreading varies with the vaccination rate.\\
\end{itemize}

\textbf{Connect Four AI} \hfill \textit{Jun.--Aug.2018} 
\vspace*{1mm}\\
{Independent research on Machine Learning.}
\vspace*{1mm}
\begin{itemize}
	\item A Connect4 agent based on Monte Carlo Tree Search (MCTS).
\end{itemize}

%=========================================================================
%=========================================================================
\section{Work Experience}

\textbf{University Surf Society} \textit{Trip Secretary} \hfill \textit{Jun.2022--Present}
\vspace*{1mm}
\begin{itemize}
	\item Planned and organised a 50-people surf trip to Morocco with a \$20k budget.
	\item Currently working on another 50-people trip to the Canary Islands.\\
\end{itemize}

\textbf{Physics Olympiad Tutor} \textit{Tutoring} \hfill \textit{Jun.2022--Present}
\vspace*{1mm}
\begin{itemize}
	\item Tutoring for the preparation of IPhO, BPhO and other advanced physics competition.\\
\end{itemize}

\textbf{M2 Digital Asset Management} \textit{Summer Intern} \hfill \textit{Jun.--Jul.2021}
\vspace*{1mm}\\
{Project: Research and Development of Bitcoin Pricing Models.}
\vspace*{1mm}
\begin{itemize}
	\item Estimated the average mining cost per coin from historical mining difficulty and ASIC chip efficiency data.
	\item Developed codes to estimate the probability distribution of future BTC prices by using current option prices.
\end{itemize}

%=========================================================================
%=========================================================================
\section{Programming/Computers}
{Python (Numpy, Scipy, Scikit, Tensorflow, PyTorch), C++, \LaTeX, Linux}

\section{Hobbies}
{Poker, Surfing, Skateboarding, Speed Cubing, DJing(House)}

\end{document}
%% end of file `template.tex'.